Constructing a universe for the setoid model

### 2020-07-08 paper.tex
Add paragraphs on missing formalization

Luckily, it turns out that the \emph{simple} elimination principle is sufficient
for our purposes: all functions of Section \ref{ii-universe} are defined using simple mutual pattern matching without recursion-recursion.
The simple eliminator can be defined by pattern matching on
the untyped codes, and does not require extensionality or any extra principles
beyond strong transport.

@@

We have described the construction of a universe of setoids in the setoid model
of type theory; this is given in several steps, first as an inductive-recursive
definition, then as an inductive-inductive definition, and finally as an
inductive type. Every encoding is obtained from the previous by adapting known
data type transformation methods in a novel way that accounts for the
peculiarities of our construction. The mathematical contents of this paper have
been formalized in the proof-assistant Agda (see \cite{agda-code}).

Our inductive definition of the setoid universe relies on a metatheory with a
strong transport rule. As future work, we would like to prove normalization for
this metatheory, since we don't yet know if this property holds in the presence
of such rule, and previous work in this respect \cite{abel2019failure} seems to
suggest that is represents a non-trivial addition.
%
An alternative path worth investigating is to find a construction of the
universe that does not rely on strong transport. Note that this issue only
involves the inductive definition, as the inductive-recursive and
inductive-inductive versions do not need strong transport.

>>>>

Luckily, it would seem the \emph{simple} elimination principle is sufficient for
our purposes: careful inspection of the code suggests that all functions
described in Section \ref{ii-universe} can be defined using simple mutual
pattern matching without recursion-recursion. The simple eliminator can be
defined by pattern matching on the untyped codes, and does not require
extensionality or any extra principles beyond strong transport. Note that
producing a full formalization that uses exclusively simple eliminators appears
to be extremely time-consuming; we therefore leave this task to future work.

@@

We have described the construction of a universe of setoids in the setoid model
of type theory; this is given in several steps, first as an inductive-recursive
definition, then as an inductive-inductive definition, and finally as an
inductive type. Every encoding is obtained from the previous by adapting known
data type transformation methods in a novel way that accounts for the
peculiarities of our construction.

Most of the mathematical contents of this paper have been formalized in the
proof-assistant Agda (see \cite{agda-code}). We aim to complete the
formalization in the near future, in particular to obtain a machine-checked
proof that our inductive construction of the setoid universe does not rely on
recursion-recursion.

The inductive definition of the universe relies on a metatheory with a strong
transport rule. As future work, we would like to prove normalization for this
metatheory, since we don't yet know if this property holds in the presence of
such rule, and previous work in this respect \cite{abel2019failure} seems to
suggest that is represents a non-trivial addition.
%
An alternative path worth investigating is to find a construction of the
universe that does not rely on strong transport. Note that this issue only
involves the inductive definition, as the inductive-recursive and
inductive-inductive versions do not need strong transport.
